\documentclass[overlapped,centered]{resume}
\usepackage{hyperref}

\begin{document}

\name{\Large Amber Jain's \Resume \footnote{The latest version of this resume is available at \url{http://amberja.in/resume.html}}}

\address{Growth Engineering, Inbound Marketing, Backend/DevOps}

\begin{resume}
    % Contact Information
    \section{\mysidestyle Contact}
    \begin{tabular}{@{} l @{\hspace{68mm}} r}
    http://amberja.in/ & i.amber.jain@gmail.com/(+91)97691-10914
	%Mumbai, India & (+91) 97691-10914 \\
    \end{tabular}

    % Academic/Research Interests
    %\section{\mysidestyle Interests}

    %\textbf{Backend Development, DevOps, Growth Hacking}

    % Professional Experience
    \section{\mysidestyle Employment}

    \begin{list2}
    
    \item \textbf{CEO/Cofounder - HashGrowth.com} (Y Combinator SUS17) \hspace{20mm} \textbf{August 2016 - now} \\ Lead Product \& Growth for a SaaS product to drive organic reach of mobile apps on Play/App Store using Analytics, Keywords Research \& Insights.
    
	\setlength{\leftskip}{15pt}
	
		- Bootstraped \& built the SaaS product with a team of 3 using Python, Django, PostgreSQL, HAProxy, RabbitMQ, Celery, uWSGI, Nginx, AWS etc.
 
		- Lead B2B growth by increasing customer base from from 0 to first 50 companies within a month of private beta launch.
 
 		- Optimized the backend \& AWS infrastructure to handle over 300,000 API hits on a daily basis in a monthly budget of \$300 on AWS.
 
		- Sourced over 200 servers (each costing less than USD 6 per year) \& setup infrastructure on them to bypass the throttling imposed by Google on scraping the data of around 3 million apps on Play Store.

	\setlength{\leftskip}{0pt}

    \item \textbf{Founder - ViralCents \hspace{75mm} Feb 2016 - May 2016} \\ B2B2C product for incentivized social sharing of advertisor's content by publishers on social media.
    
    \item \textbf{Growth \& DevOps Engineer - Taskbob.com \hspace{45mm} Apr 2015 - Dec 2015} \\ Growth \& Backend Engineering in Python. Setup and automation of systems infrastructure running on AWS (EC2, S3, CloudFront, RDS etc); ElasticSearch Logstash Kibana (ELK) for log management.
    
    \item \textbf{DevOps Engineer - Tinyowl.com \hspace{65mm} Jan 2014 - Nov 2014} \\ Setup and automation of systems infrastructure Ruby on Rails, Ubuntu server, Nginx, Passenger, PostgreSQL, PostGIS, MongoDB, ElasticSearch, Memcached, Redis, Resque, Ansible, Sentry, Docker, Python, BeautifulSoup, Locust, ACRA, AWS (EC2, S3, Autoscaling, ELB, CloudFront, VPC, CloudWatch, IAM, CloudFormation), log management (logrotate, AWS S3, ElasticSearch, GrayLog2, Logstash).
    
	\item \textbf{Google Summer of Code - OpenCog Foundation \hspace{35mm} May 2012 - Aug 2012} \\ Fully automated build, packaging and deployment of OpenCog instances for Linux and Cygwin port.

	\item \textbf{System Administrator - iips.edu.in \hspace{60mm} Sep 2012 - Mar 2013} \\ Sysadmin and developer at e-governance center at International Institute of Professional Studies (D. A. University).

	\end{list2}

    % Growth Projects
    \section{\mysidestyle Growth Projects} 
	\begin{list2}
	
	\item \textbf{Quora/Pinterest/Medium Automation}: Set of scripts to piggyback on Quora, Pinterest or Medium traffic by automatically creating hundreds of Q\&As or blogposts daily, to drive thousands of additional pageviews every week.
	
	\item \textbf{Hurricane IP}: Product that generates tens of thousands of unique IPs daily. Comes with a set of scripts catering to needs of digital marketing \& data scraping companies.
	
	\item \textbf{MacAppStore.org}: Optimized the site for SEO with \$0 marketing budget, which now brings organic 165,000 pageviews every month:

	\setlength{\leftskip}{15pt}
	
		- Content for over ~5100 pages created automatically using a script. 
	
		- Over 165,000 pageviews every month, with 90\% traffic being organic (from Google).
		
		- Generates ~USD80-100 revenue every month from affiliate programs.
	
		- 50\% traffic from USA, UK, Germany, France, Canada, Japan and China.
	
		- Over 3000 organic backlinks.from high Domain Authority (DA) websites.
	
		- High authority website on Google (one of Alexa Top 100000 websites).
	
	\setlength{\leftskip}{0pt}
	
	\item \textbf{HashGrowth.com}: SaaS platform for App Store Optimization (ASO) to drive growth of mobile apps using Analytics, Keywords Research \& Insights for Google Play Store and Apple App Store.
	
	\item \textbf{Other Growth Projects}: I have worked on a bunch of other growth engineering projects, which I can discuss only off-the-record (due to ethics and/or client confidentiality) during the interview.
	
	\end{list2}
	
	% Skills
    \section{\mysidestyle Skills} 

    \begin{list2}
	\item \textbf{Programming}: Python, Django, Flask, Bootstrap, HTML, CSS, Javascript, Ansible, bash, MATLAB/Octave, C
	\item \textbf{Data stores}: PostgreSQL/MySQL, SQLite,	MongoDB, Redis
	\item \textbf{Systems}: Nginx/Apache, HAProxy, Passenger/uWSGI/Gunicorn, Ubuntu/Debian Server, AWS, Google Cloud, Microsoft Azure, Sentry, ElasticSearch/Logstash/Kibana (ELK), Docker, Cygwin, (c)make
	\end{list2}

    % Engineering Projects
    \section{\mysidestyle Engineering Projects} 
	\begin{list2}
	
	\item \textbf{ML projects}: Implemented Machine Learning algorithms for automated handwritten digit recognition, spam classifier, image compression etc. in Octave/MATLAB for Coursera's Machine Learning class.
	
	\item \textbf{Bulk Whatsapp Sender}: Proof-of-concept bulk whatsapp message sender by leveraging functional testing; Built with Genymotion, Appium, Python.
	
	\item \textbf{Customer Data Platform (CDP)}: Hackathon project to aggregate data from 3rd party profile enrichment services (augur.io, 360social.me, foursquare etc.) Made in Python, BeautifulSoup.
	
	\item \textbf{Time Your Instagram}\footnote{Time Your Instagram \url{http://amberja.in:9000/}}: Suggests optimal time for Instagram posts (Python/Flask/requests/Bootstrap).
	
	\item \textbf{MOOC posters}\footnote{MOOC Posters: \url{http://mooc-posters.in/}}: Full stack development of Python/Django website to generate printable PDF posters for online courses from Coursera.
	
	\item \textbf{ocpkg}: Google Summer of Code project; Fully automated build, packaging \& deployment of OpenCog instances for Linux/Windows (continuous as well as on-demand build generation).
	
	\item \textbf{udacity-cs101}: Implemented a web crawler and search engine in Python for Udacity's CS101 course.
	
    \end{list2}

	% Talks
	\section{\mysidestyle Talk(s)}
	\begin{list2}
	\item \textbf{Facts \& Fallacies about Growth Hacking} at BarCamp Bangalore (Feb 2018)
	\item \textbf{Design for Non-designers} at BarCamp Mumbai (Dec 2014)
	\end{list2}

    % Certifications \\ *- ONGOING
    \section{\mysidestyle Certificates}

    \begin{list2}
    % Coursera
	\item \textbf{Machine Learning} (Stanford University) \hspace{38mm} \textbf{77/80 (HW), 800/800 (Coding)}
	
	\item \textbf{CS271: Introduction to Artificial Intelligence} (Udacity) \hspace{52mm} \textbf{91.7\%}
	
	% Coursera
	\item \textbf{Startup Engineering} (Stanford University) \hspace{78mm} \textbf{83.4\%}
	
    % Coursera
    \item \textbf{Gamification} (University of Pennsylvania) \hspace{47mm} \textbf{98\% (Verified Certificate)}
	
	% Coursera
	\item \textbf{Computing for Data Analysis} (Johns Hopkins University) \hspace{28mm} \textbf{99\% with Distinction}

	% Class2Go
	\item \textbf{Introduction to Databases} (Stanford University) \hspace{46mm} \textbf{225.0 out of 293.0}

	\item \textbf{CS101: Introduction to Computer Science} (Udacity) \hspace{34mm} \textbf{Highest Distinction}
	
	% Coursera
    \item \textbf{Model Thinking} (University of Michigan) \hspace{44mm} \textbf{91.1\% (Verified Certificate)}

	% Coursera
	\item \textbf{Networked Life} (University of Pennsylvania) \hspace{77mm} \textbf{95.6\%}

	% Coursera
	\item \textbf{Writing in the Sciences} (Stanford University) \hspace{45mm} \textbf{97.8\% with Distinction}
	\end{list2}

    % Education \\ *- ONGOING
    \section{\mysidestyle Education}

    \begin{list2}
	\item \textbf{Master of Computer Applications}, MCA (D.A. University, May 2013) \hspace{16mm} \textbf{CGPA: 7.84/10} 
	\end{list2}

	\begin{list2}
	\item \textbf{Bachelor of Computer Applications}, BCA (D.A. University, Jun 2010) \hspace{15mm} \textbf{CGPA: 7.55/10}
	\end{list2}

    % Miscellaneous
    \section{\mysidestyle Hobbies}
    \begin{list2}
    \item Reading Books, cycling, badminton, writing/blogging, swimming, hockey.
    %\item Languages: English, Hindi
    %\item Citizenship: India
    %\item Relocation preference: Willing to work remotely or relocate to a new city/country.
     
    \end{list2}

\end{resume}
\end{document}
