\documentclass[margin,line]{resume}
\usepackage{hyperref}

\begin{document}

\name{\Large Amber Jain's \Resume \footnote{The latest version of this resume is available at \url{http://amberja.in/resume.html}}}

\begin{resume}

    % Contact Information
    \section{\mysidestyle Contact}
    \begin{tabular}{@{} l @{\hspace{68mm}} r}
    http://amberja.in/ & i.amber.jain@gmail.com/(+91)97691-10914
	%Mumbai, India & (+91) 97691-10914 \\
    \end{tabular}

    % Academic/Research Interests
    %\section{\mysidestyle Interests}

    %\textbf{Backend Development, DevOps, Growth Hacking}

    % Professional Experience
    \section{\mysidestyle Employment}

    \begin{list2}
    
    \item \textbf{CEO/Cofounder - HashGrowth.com (Y Combinator SUS17)} \hspace{25mm} August 2016 - now \\ Analytics, Keyword Research \& Insights for App Stores to drive organic mobile growth (SaaS MarTech).
    
    \item \textbf{Founder - Viralcents.com} \hspace{82mm} Feb 2016 - May 2016 \\ B2B2C product for incentivized social sharing of advertisor's content by on social profile of publishers.
    
    \item \textbf{Backend/Growth Engineer - Taskbob.com} \hspace{54mm} Apr 2015 - Dec 2015 \\ Backend and growth hacking in Python. Setup and automation of systems infrastructure running on AWS; ElasticSearch Logstash Kibana (ELK) for log management.
    
    \item \textbf{DevOps Engineer - Tinyowl.com} \hspace{70mm} Jan 2014 - Nov 2014 \\ Setup and automation of systems infrastructure Ruby on Rails, Ubuntu server, Nginx, Passenger, PostgreSQL, PostGIS, MongoDB, ElasticSearch, Memcached, Redis, Resque, Ansible, Sentry, Docker, Python, BeautifulSoup, Locust, ACRA, AWS (EC2, S3, Autoscaling, ELB, CloudFront, VPC, CloudWatch, IAM, CloudFormation), log management (logrotate, AWS S3, ElasticSearch, GrayLog2, Logstash).
    
	\item \textbf{Google Summer of Code - OpenCog Foundation} \hspace{40mm} May 2012 - Aug 2012 \\ Fully automated build, packaging and deployment of OpenCog instances for Linux and Cygwin port.

	\item \textbf{Developer and Sysadmin - iips.edu.in} \hspace{60mm} Sep 2012 - Mar 2013 \\ Volunteer system administrator and developer at e-governance center at IIPS, Devi Ahilya University.

	\end{list2}

    % Projects
    \section{\mysidestyle Personal \\ Projects} 
	\begin{list2}

	\item \textbf{Play Store Keywords Tool}\footnote{Play Store Keywords Tool: \url{http://amberja.in:5000/}}: Keyword Research for App Store Optimization (ASO) on Google Play Store. Built with Flask, Python, Bootstrap, ZeroClipboard.js.
	
	\item \textbf{Time Your Instagram}\footnote{Time Your Instagram \url{http://amberja.in:9000/}}: Suggests optimal time for Instagram posts (Python/Flask/requests/Bootstrap).
	
	\item \textbf{Bulk Whatsapp Sender}: Proof-of-concept bulk whatsapp message sender by leveraging functional testing; Uses Genymotion, Appium, Python.
	
	\item \textbf{Customer Data Platform (CDP)}: Hackathon project to aggregate data from 3rd party profile enrichment services (augur.io, 360social.me, foursquare etc.) Made in Python, BeautifulSoup.
	
	\item \textbf{MOOC posters}\footnote{MOOC Posters: \url{http://mooc-posters.in/}}: Full stack development of Python/Django website to generate printable PDF posters for online courses from Coursera.
	
	\item \textbf{ocpkg}: Google Summer of Code project; Fully automated build, packaging \& deployment of OpenCog instances for Linux/Windows (continuous as well as on-demand build generation).
	
	\item \textbf{udacity-cs101}: Implemented a web crawler and search engine in Python for Udacity's CS101 course.
	
	\item \textbf{ml-class}: Implemented Machine Learning algorithms for automated handwritten digit recognition, spam classifier, image compression etc. in Octave/MATLAB for Coursera's Machine Learning class.
	
    \end{list2}

	% Talks
	\section{\mysidestyle Talk(s)}
	\begin{list2}
	\item \textbf{Design for Non-designers} at BarCamp Mumbai (Dec 2014)
	\end{list2}

    % Skills
    \section{\mysidestyle Skills} 

    \begin{list2}
	\item \textbf{Programming/Scripting}: \hspace{2mm} Python, Django, Flask, Bootstrap, HTML, CSS, Javascript, Ansible, bash, MATLAB/Octave, C
	\item \textbf{Databases/Serialization}: \hspace{4.4mm} PostgreSQL, SQLite,	MongoDB, Redis, JSON
	\item \textbf{Systems}: \hspace{32mm}  Nginx/Apache, Passenger/UWSGI/Gunicorn, Ubuntu Server, AWS, Google Cloud, Azure, Docker, Sentry, ElasticSearch/Logstash/Kibana (ELK), Cygwin, (c)make
	\end{list2}

    % Certifications \\ *- ONGOING
    \section{\mysidestyle Certificates}

    \begin{list2}
    \item \textbf{Gamification} (Coursera) \hspace{74mm} \textbf{98\% (Verified Certificate)}
    
	\item \textbf{Startup Engineering} (Coursera) \hspace{94mm} \textbf{83.4\%}

	\item \textbf{Introduction to Databases} (Class2Go) \hspace{64mm} \textbf{225.0 out of 293.0}

	\item \textbf{CS101: Introduction to Computer Science} (Udacity) \hspace{34mm} \textbf{Highest Distinction}

	\item \textbf{Machine Learning} (Coursera) \hspace{54mm} \textbf{77/80 (HW), 800/800 (Coding)}

	\item \textbf{CS271: Introduction to Artificial Intelligence} (Udacity) \hspace{52mm} \textbf{91.7\%}

	\item \textbf{Networked Life} (Coursera) \hspace{104mm} \textbf{95.6\%}

	\item \textbf{Computing for Data Analysis} (Coursera) \hspace{52mm} \textbf{99\% with Distinction}

    \item \textbf{Model Thinking} (Coursera) \hspace{65mm} \textbf{91.1\% (Verified Certificate)}

	\item \textbf{Writing in the Sciences} (Coursera) \hspace{60mm} \textbf{97.8\% with Distinction}
	\end{list2}

    % Education \\ *- ONGOING
    \section{\mysidestyle Education}

    \begin{list2}
	\item \textbf{Master of Computer Applications} MCA (D.A. University, May 2013) \hspace{16mm} \textbf{CGPA: 7.84/10} 
	\end{list2}

	\begin{list2}
	\item \textbf{Bachelor of Computer Applications} BCA (D.A. University, Jun 2010) \hspace{15mm} \textbf{CGPA: 7.55/10}
	\end{list2}

    % Miscellaneous
    \section{\mysidestyle Hobbies}
    \begin{list2}
    \item Reading Books, Blogging, Swimming, Hockey, Table Tennis, Badminton
    %\item Languages: English, Hindi
    %\item Citizenship: India
    %\item Relocation preference: Willing to work remotely or relocate to a new city/country.
     
    \end{list2}

\end{resume}
\end{document}
